Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-09 paper.tex
Add sim results.

TODO

>>>>

We simulated 100 trials for rewiring values of 0.0, 0.167, 0.333, 0.5, 0.667, 0.833, and 1.0.
For each trial we generated an NK model with N=250 and K=7 and ran each social learning strategy
for 300 iterations,
as well as a network based on that NK model and rewired.
We confirmed that all trials converged to their maximum value before reaching the last iteration.
Some statistics on the network properties of the networks are summarized in Table \ref{tab:stats}.
We see that the coefficient of variation of degree is approimately 10\%,
while only 1\% for mean path length, confirming that the rewiring process has a stronger influence
on degree than on path length.

\begin{table}
\small
\centering
\caption{
Simulated network statistics.
\label{tab:stats}
}
\bigskip
\begin{tabular}{lcc}
\hline
Property          & Mean  & Std. Dev. \\
\hline
Mean Degree       & 132.3 & 9.2 \\
Mean Path length  & 1.735 & 0.019 \\
\hline
\end{tabular}
\end{table}

Figure \ref{fig:val-iter} shows how agents' solutions improve after repeated applications of
different learning strategies and rewiring values.
Each curve represents an average over 100 trials, each with 250 agent solutions.
For all rewiring values, local strategies are less efficient and more performant than their
nonlocal counterparts.
The consensus strategy is both more efficient and more performant than others,
with its performance increasing with higher rewiring.

The effect of degree on performance and efficiency is shown in Figure \ref{fig:deg-eff-perf} and
Tables \ref{tab:sim-eff} and \ref{tab:sim-perf}.
For both local and nonlocal versions of the best-neighbor and conformity strategies,
there is no significant effect of degree on performance or efficiency.
As noted above however, the local versions consistently have higher performance and lower efficiency
than their nonlocal counterparts.
We observe more interesting behavior with the consensus strategy.
Node degree shows a significant negative correlation with degree,
and a small but significant positive correlation with efficiency.
The consensus simulations replicate the efficiency behavior observed in WikiProjects,
but the opposite behavior for performance.
But unlike other strategies, consensus demonstrates that degree distribution can have an
impact on both performance and efficiency.
